\documentclass[a4paper,12pt]{article}


% add more packages if necessary
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{epstopdf}

% TODO: Add your group name
\newcommand{\groupname}{Badgers\xspace}


\title{
Project Report \\ 
Group \groupname \\
\vspace{5mm}
\large Java and C\# in depth, Spring 2013
}
\author{
% TODO: Add your names here
Thomas Frick (03-150-927)\\
Matthias Ganz (04-862-850)\\
Philipp Rohr (04-397-030)
}
\date{\today}

\begin{document}
\maketitle


\section{Introduction}

This document describes the design and implementation of the \emph{Personal
Virtual File System} of group \emph{\groupname}. The project is part of the
course \emph{Java and C\# in depth} at ETH Zurich. The following sections
describe each project phase, listing the requirements that were implemented and
the design decisions taken. The last section describes a use case of using the
\emph{Personal Virtual File System}.

% PART I: VFS CORE
% --------------------------------------

\section{VFS Core}

VFS Core is a library that provides an implementation of a virtual file system.
The API that a client of this library can use consists of three interfaces that
are described in \ref{sec:coreClasses}. The VFS Core provides functionality to
create/open/dispose new virtual disks and allows the management of files and
directories within such a disk. Furthermore it provides a simple way to
import/export files from/to the host file system.

The library internally works with a virtual disk that is divided into a header,
index and data section, having the index represented as B-tree. Such a design
allows quick access to the data on the disk.


\include{01requirements}
\include{02design}
\include{03fileformat}

% PART II: VFS Browser
% --------------------------------------

\section{VFS Browser}

VFS Browser is a JAVA Swing application atop the VFS core. The browser was
developed during the second milestone of the project. The main goal of the
browser application is to give users a convenient access to their virtual disks.
It allows browsing files and folders, as well as importing and
exporting from/to the host filesystems. Additionally it provides a convenient
search interface, that allows quick finding of files.


\include{11requirements}
\include{12design}
\include{13integration}


% PART III: Synchronization Server
% --------------------------------------

\section{Synchronization Server}

Synchronization Server is a command line server that allows synchronization of
virtual disks. It allows basic user management via VFS Browser, that includes
creating users and a login of created users. Logged in users can link local
disks to an account on the server via VFS Browser and then can connect to such
shared disks from an other client machine. Disks can also be created directly on
the server. When VFS Browser has a connection to the server, changes that occur
on the local disk will be propagated to the server which propagates these
changes to possibly other connected machines. If a user has
no connection to the Synchronization Server but operates on a disk that is
linked to a server instance the changes are recorded and are propagated as soon
as the connection is established next time. Thus synchronization server allows
seamless synchronization between several VFS Browser instances running on
different machines.



\include{21requirements}
\include{22design}
\include{23integration}


\include{04quickstart}
\include{05glossary}

\bibliographystyle{plain}
\bibliography{literature}
\end{document}
