\subsection{Requirements}
Below one will find a list of the requirements implemented in this project.

\subsubsection {Basic Requirements}
\begin{itemize}
  \item \emph{The browser should be implemented on one of the following
  platforms: desktop, web or mobile}
  \item \emph{The browser should support all operations from Part 1 (VFS core).
  For example, users should be able to select a file/folder and copy it to
  another location without using console commands. }
  \item \emph{The browser should support both single and multiple selection of
  files/folders.}
  \item \emph{The browser should support keyboard navigation. The mandatory set of operations includes folder
  navigation, going to parent and child folders (this is optional for mobile applications due to limited
  keyboard functionality).}
  \item \emph{The browser should support mouse navigation (or touch in case of the mobile platform). The
  required operations are the same as in requirement 4.}
  \item \emph{The browser should support file-name search based on user-given
  keybwords. The search should provide options for: case sensitive/ case
  insensitive search; restrict search to folder; restrict search to folder and subfolders.}
\end{itemize}  These requirements are met with the classes
\begin{verbatim}
ch.eth.jcd.badgers.vfs.ui.desktop.view.BadgerMainFrame
ch.eth.jcd.badgers.vfs.ui.desktop.view.BadgerMenuBar
ch.eth.jcd.badgers.vfs.ui.desktop.view.BadgerTable
ch.eth.jcd.badgers.vfs.ui.desktop.view.DiskSpaceDialog
ch.eth.jcd.badgers.vfs.ui.desktop.view.ImportDialog
ch.eth.jcd.badgers.vfs.ui.desktop.view.NewDiskCreationDialog
\end{verbatim} provide the frontend functionalities to meet the requirements

\begin{verbatim}
ch.eth.jcd.badgers.vfs.ui.desktop.model.BadgerFileExtensionFilter
ch.eth.jcd.badgers.vfs.ui.desktop.model.EntryTableModel
ch.eth.jcd.badgers.vfs.ui.desktop.model.EntryUiModel
ch.eth.jcd.badgers.vfs.ui.desktop.model.ParentFolderEntryUiModel
\end{verbatim} are the model classes, that model table entries and ui models

\begin{verbatim}
ch.eth.jcd.badgers.vfs.ui.desktop.controller.BadgerController.java
ch.eth.jcd.badgers.vfs.ui.desktop.controller.BadgerViewBase.java
ch.eth.jcd.badgers.vfs.ui.desktop.controller.DesktopController.java
ch.eth.jcd.badgers.vfs.ui.desktop.controller.SearchController.java
ch.eth.jcd.badgers.vfs.ui.desktop.controller.WorkerController.java
\end{verbatim} provide the controller classes of a typical MVC design. 


\subsubsection {Implemented Bonus Requirements}
\begin{itemize}
  \item \emph{Responsive UI, i.e. the browser does not stall during long-running
  operations (i.e. file search or import).} Is implemented with decoupling the
  disk work from the gui work. This is done with a single thread accessing the
  disk api. This thread has a work queue to which \textit{Actions} are added.
  \item \emph{Advanced search; For example, search with wildcards.} For this the
  API had to be extended slightly.
  \item \emph{Drag-and-drop for manipulative operations (import).} For that we
  register a \textit{DropTarget} on the \textit{BadgerTable} that has a
  \textit{DropTargetListener} which starts the import on the
  \textit{DesktopController}.
\end{itemize}

\subsubsection {Not Implemented Bonus Requirements}
\begin{itemize}
  \item \emph{Nice-to-have features like operation progress report (e.g. the
  number of files processed during export) or drag-and-drop for manipulative
  operations (move, copy).}
  \item \emph{The browser is implemented for an additional platform}
  \item \emph{Efficient full-text search (using some sort of indexing).}
\end{itemize}
