\subsection{Requirements}
Below one will find a list of the requirements implemented in this project.

\subsubsection {Requirements for the browser}
\begin{itemize}
  \item \emph{The browser should allow the user to create a new account or to log in to an existing account.}
  \item \emph{The browser should offer to switch to an online mode, and be able
  to operate without a connection to the server. }
  \item \emph{The browser should support binding an existing virtual disk to an active account.}
\end{itemize}  


\subsubsection {Requirements for the server}
\begin{itemize}
  \item \emph{The server should support registration of unique accounts. Each
  account includes name \& password.}
  \item \emph{The server should track changes to linked virtual disks of registered accounts and synchronize the
changes across the machines.}
\end{itemize}  


\subsubsection {Implemented Bonus Requirements}
\begin{itemize}
  \item \emph{Provide a set of mocked unit tests for your implementation.}

  \item \emph{Conflict Resolution: implement a conflict resolution scheme, so
  that concurrent changes to the same file are not lost (e.g. saving conflicting
  files as separate versions).}
  \item \emph{The browser is updating automatically when changes to the disk
  occur.}
  \item \emph{The server is able to synchronize changes, which are done
  simultaneously on the same account on different machines}
 
\end{itemize}

\subsubsection {Not Implemented Bonus Requirements}
\begin{itemize}
  \item \emph{File History: provide a history for files and an interface to
  restore a previous version}
 \item \emph{Incremental Changes: minimize the communication between the browser
 and the server by only transferring the parts of a file that changed.}
\end{itemize}
